PineAPPL: EW and mixed QCD--EW corrections for PDF fits

### 2020-07-29 paper/app-pineappl.tex
Fix missing reference

SUBCOMMANDS:
    channels           Shows the contribution for each partonic channel
    convolute          Convolutes a PineAPPL grid with a PDF set
    help               Prints this message or the help of the given
                       subcommand(s)
    luminosity         Shows the luminosity function
    merge              Merges one or more PineAPPL grids together
    orders             Shows the predictions for all bins for each order
                       separately
    pdf_uncertainty    Calculates PDF uncertainties
\end{lstlisting}
As an example we show the grid produced for the ATLAS DY high-mass lepton-pair production (from section~\ref{sec:atlas-high-mass-dy}).
The output shows all 13 bins with lower (\texttt{xmin}) and upper limit (\texttt{xmax}) of the invariant mass $M_{\ell \bar{\ell}}$ of the lepton pair, with the differential cross section $\mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ (\texttt{diff}), integrated cross section $(M_{\ell \bar{\ell}}^\mathrm{max} - M_{\ell \bar{\ell}}^\mathrm{min}) \mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ (\texttt{integ}), together with the perturbative uncertainty estimated from a 7-point scale variation (\texttt{neg unc} and \texttt{pos unc}).
\begin{lstlisting}[language=bash]
 $ pineappl convolute ATLASZHIGHMASS49FB.pineappl \
 > NNPDF31_nlo_as_0118_luxqed
bin xmin xmax     diff        integ     neg unc pos unc
---+----+----+------------+------------+-------+-------
  0  116  130 2.0630698e-1  2.8882978e0  -2.08%   1.69%
  1  130  150 9.1818985e-2  1.8363797e0  -1.79%   1.86%
  2  150  170 4.5306370e-2 9.0612740e-1  -1.60%   1.98%
  3  170  190 2.5894856e-2 5.1789712e-1  -1.66%   2.06%
  4  190  210 1.6075267e-2 3.2150534e-1  -1.70%   2.10%
  5  210  230 1.0526659e-2 2.1053317e-1  -1.71%   2.12%
  6  230  250 7.1928162e-3 1.4385632e-1  -1.71%   2.13%
  7  250  300 4.0776555e-3 2.0388277e-1  -1.70%   2.44%
  8  300  400 1.4775481e-3 1.4775481e-1  -1.94%   2.87%
  9  400  500 4.5473785e-4 4.5473785e-2  -2.30%   3.19%
 10  500  700 1.2164277e-4 2.4328555e-2  -2.41%   3.12%
 11  700 1000 1.9792340e-5 5.9377019e-3  -2.05%   2.12%
 12 1000 1500 2.0228761e-6 1.0114381e-3  -1.29%   0.47%
\end{lstlisting}

@@

The following run card was used to produce the results shown in section~\ref{sec:atlas-high-mass-dy}.
The only difference to a normal \textsc{mg5\_aMC@NLO} run is the switch \texttt{set iappl 1}, which enables filling a \textsc{PineAPPL} grid.
For a complete set of runcards and patches see TODO.

>>>>

SUBCOMMANDS:
    channels           Shows the contribution for each partonic channel
    convolute          Convolutes a PineAPPL grid with a PDF set
    help               Prints this message or the help of the given
                       subcommand(s)
    luminosity         Shows the luminosity function
    merge              Merges one or more PineAPPL grids together
    orders             Shows the predictions for all bins for each order
                       separately
    pdf_uncertainty    Calculates PDF uncertainties
\end{lstlisting}
As an example we show the grid produced for the ATLAS DY high-mass lepton-pair production (from section~\ref{subsec:numerical_results}).
The output shows all 13 bins with lower (\texttt{xmin}) and upper limit (\texttt{xmax}) of the invariant mass $M_{\ell \bar{\ell}}$ of the lepton pair, with the differential cross section $\mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ (\texttt{diff}), integrated cross section $(M_{\ell \bar{\ell}}^\mathrm{max} - M_{\ell \bar{\ell}}^\mathrm{min}) \mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ (\texttt{integ}), together with the perturbative uncertainty estimated from a 7-point scale variation (\texttt{neg unc} and \texttt{pos unc}).
\begin{lstlisting}[language=bash]
 $ pineappl convolute ATLASZHIGHMASS49FB.pineappl \
 > NNPDF31_nlo_as_0118_luxqed
bin xmin xmax     diff        integ     neg unc pos unc
---+----+----+------------+------------+-------+-------
  0  116  130 2.0630698e-1  2.8882978e0  -2.08%   1.69%
  1  130  150 9.1818985e-2  1.8363797e0  -1.79%   1.86%
  2  150  170 4.5306370e-2 9.0612740e-1  -1.60%   1.98%
  3  170  190 2.5894856e-2 5.1789712e-1  -1.66%   2.06%
  4  190  210 1.6075267e-2 3.2150534e-1  -1.70%   2.10%
  5  210  230 1.0526659e-2 2.1053317e-1  -1.71%   2.12%
  6  230  250 7.1928162e-3 1.4385632e-1  -1.71%   2.13%
  7  250  300 4.0776555e-3 2.0388277e-1  -1.70%   2.44%
  8  300  400 1.4775481e-3 1.4775481e-1  -1.94%   2.87%
  9  400  500 4.5473785e-4 4.5473785e-2  -2.30%   3.19%
 10  500  700 1.2164277e-4 2.4328555e-2  -2.41%   3.12%
 11  700 1000 1.9792340e-5 5.9377019e-3  -2.05%   2.12%
 12 1000 1500 2.0228761e-6 1.0114381e-3  -1.29%   0.47%
\end{lstlisting}

@@

The following run card was used to produce the results shown in section~\ref{subsec:numerical_results}.
The only difference to a normal \textsc{mg5\_aMC@NLO} run is the switch \texttt{set iappl 1}, which enables filling a \textsc{PineAPPL} grid.
For a complete set of runcards and patches see TODO.

### 2020-07-29 paper/sec-pineappl.tex
Fix missing reference

Using 4-tuples has the clear advantage of being very easy to implement and test.
Furthermore, they reproduce the exact numerical value that is also calculated by the MC integrator.
However, the price one has to pay is the size of the 4-tuples.
To give a concrete example, NLO QCD+EW Drell--Yan lepton-pair production (see section~\ref{sec:pineappl-example} and section~\ref{sec:atlas-high-mass-dy}) needs \SI{159}{\giga\byte} of storage for a target precision of \SI{1}{\percent} of the integrated cross section.
While this is an acceptable size, increasing the precision by an order of magnitude would require roughly 100 times the size, due to the Monte Carlo convergence that goes as $1/\sqrt{N}$ with $N$ being the number of 4-tuples.
With increasing size also the speed of the convolution degrades, because it basically becomes bound by the speed with which the 4-tuples can be read from disk.
However, due to the uncompressed nature of this representation it can serve as a intermediate format to develop and quickly cross check more space-efficient representations, which we will discuss next.

>>>>

Using 4-tuples has the clear advantage of being very easy to implement and test.
Furthermore, they reproduce the exact numerical value that is also calculated by the MC integrator.
However, the price one has to pay is the size of the 4-tuples.
To give a concrete example, NLO QCD+EW Drell--Yan lepton-pair production (see section~\ref{sec:pineappl-example} and section~\ref{subsec:numerical_results}) needs \SI{159}{\giga\byte} of storage for a target precision of \SI{1}{\percent} of the integrated cross section.
While this is an acceptable size, increasing the precision by an order of magnitude would require roughly 100 times the size, due to the Monte Carlo convergence that goes as $1/\sqrt{N}$ with $N$ being the number of 4-tuples.
With increasing size also the speed of the convolution degrades, because it basically becomes bound by the speed with which the 4-tuples can be read from disk.
However, due to the uncompressed nature of this representation it can serve as a intermediate format to develop and quickly cross check more space-efficient representations, which we will discuss next.
